Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-18 sections/model.tex
Added subsection 3.3 Glacier bed interface

%\subsection{Glacier bed interface}
%
%The ice-sheet bed topography responds to the ice-loads following a regional isostasy model with flexure and relaxation.
%
%Geothermal heat flux is prescribed to 70\,\unit{W\,m^{-2}}
%
\subsection{Simulation design and numerical implementation}

>>>>

\subsection{Glacier bed interface}

The glacier bed topography response to the ice load is computed by a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}. To compute basal temperatures with higher accuracy, the thermal model is extended 1\,km into the bedrock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as basal condition to this model.

\subsection{Simulation design and numerical implementation}
